---
title: "CompareComputeTime"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CompareComputeTime}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dbsubsampling)
library(ggplot2)
library(tidyr)
```

We compare some methods based on `R`, `Rcpp` and `RcppArmadillo` by execueted IBOSS and OSS.

For some tasks C++ have awesome faster execution efficient than base R, RcppArmaillo provides a API for Armadillo (C++ library for linear algebra & scientific computing) which contains some convenient and efficient algorithm.

For the same task, different implementation methods may bring different speeds, and we have made a simple comparison here.

**Generate data:**
```{r generate data}
N <- 100000; d <- 7
sigma_norm <-  matrix(0.5, d, d) + diag(0.5, d)
beta_true <-  matrix(0.5, d, 1)
X <- withr::with_seed(123, mvtnorm::rmvnorm(N, mean = rep(0, d), sigma = sigma_norm))
```

# IBOSS
`IBOSS` used as the user interface for this package, but we also write some functions based on different styles to compare the computation efficiency.

- `myR_IBOSS`: Written by the package itself use `base R`.
- `myRcpp_IBOSS`: Written by the package itself use `Rcpp` like r style (Vectorization as far as possible).
- `myRcpp_cstyle_IBOSS`:  Written by the package itself use `Rcpp` like C++ style (loops for scalar as far as possible).
- `myArma_IBOSS`: Written by the package itself use `RcppArmadillo` like r style (Vectorization as far as possible).
- `IBOSS`: Quoted from [Yu et.al.(2022)](https://www.tandfonline.com/doi/suppl/10.1080/01621459.2020.1773832?scroll=top) (core code adapted from [Wang et.al.(2019)](https://github.com/Ossifragus/IBOSS)) which use Rcpp but core code is C++ style (mainly loops against scalars).

```{r IBOSS}
Size <- c(100, 200, 500, 750, 1000, 2000, 5000, 7500, 10000,  15000, 20000)

time_IBOSS <- numeric(length(Size))
time_myR_IBOSS <- numeric(length(Size))
time_myRcpp_IBOSS <- numeric(length(Size))
time_myArma_IBOSS <- numeric(length(Size))
time_myRcpp_cstyle_IBOSS <- numeric(length(Size))
for (i in seq_along(Size)){
  # paste0("Size: ", Size[i])
  begin <- Sys.time(); index <- IBOSS(Size[i], X); time_IBOSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myR_IBOSS(Size[i], X); time_myR_IBOSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myRcpp_IBOSS(Size[i], X); time_myRcpp_IBOSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myArma_IBOSS(Size[i], X); time_myArma_IBOSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myRcpp_cstyle_IBOSS(Size[i], X); time_myRcpp_cstyle_IBOSS[i] <- Sys.time() - begin;
}

time_IBOSS <- data.frame(Size, time_IBOSS, time_myR_IBOSS, time_myRcpp_IBOSS, 
                         time_myArma_IBOSS, time_myRcpp_cstyle_IBOSS)
time_IBOSS <- time_IBOSS %>% 
  pivot_longer(-Size, names_to = "Method", values_to = "Time")
ggplot(data = time_IBOSS, aes(x = Size, y = Time, group = Method, color = Method)) +
  geom_line()
```

IBOSS is relatively simple and does not require much computation of the row. The use of C++ does not seem to improve efficiency significantly, from slow to fast:

- `myRcpp_IBOSS`: Although Rcpp is used, it does not use too many C++ features, mainly vector operations, many steps inside the function have not been optimized, and the efficiency is low.
- `myRcpp_cstyle_IBOSS`: Using Rcpp with C++ features, heavy use of loops. The efficiency is not high, possibly because there are many custom functions inside the function, and the implementation method is not efficient enough.
- `myArma_IBOSS`: Despite the use of RcppArmadillo, the function interior is still R-style and does not take advantage of C++ effects.
- `myR_IBOSS`: Make use of R's native functions as much as possible, and use its internal compilation optimization to improve the computation speed.
- `IBOSS`: Although called in Rcpp form, its internal functions are written in C++ style and mainly loop over scalars. The calculation speed is remarkably fast.

# OSS
`OSS` used as the user interface for this package, but we also write some functions based on different styles to compare the computation efficiency.

- `OSS`: Written by the package itself use `Rcpp`.
- `myR_OSS`: Written by the package itself use `base R`.
- `myArma_OSS`:  Quoted from [Zhu et.al.(2023)](https://www.tandfonline.com/doi/suppl/10.1080/10618600.2023.2301093?scroll=top) which use RcppArmadillo.

```{r OSS}
Size <- c(100, 200, 500, 750, 1000)

time_OSS <- numeric(length(Size))
time_myR_OSS <- numeric(length(Size))
time_myArma_OSS <- numeric(length(Size))
for (i in seq_along(Size)){
  # paste0("Size: ", Size[i])
  begin <- Sys.time(); index <- OSS(Size[i], X); time_OSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myR_OSS(Size[i], X); time_myR_OSS[i] <- Sys.time() - begin;
  begin <- Sys.time(); index <- myArma_OSS(Size[i], X); time_myArma_OSS[i] <- Sys.time() - begin
}

time_OSS <- data.frame(Size, time_OSS, time_myR_OSS, time_myArma_OSS)
time_OSS <- time_OSS %>% 
  pivot_longer(-Size, names_to = "Method", values_to = "Time")
ggplot(data = time_OSS, aes(x = Size, y = Time, group = Method, color = Method)) +
  geom_line()
```

OSS contains a large number of loops on rows and has dynamics vector changes. The advantages of C++ are obvious, from slow to fast:

- `myR_OSS`: R is not good at looping (memory allocation in loops leads to slow speeds) and is not good at handling dynamic vector changes.
- `OSS`: Using Rcpp significantly increases speed.
- `myArma_OSS`: RcppArmadillo calls C++ Armadillo library, the internal algorithm is more efficient, more suitable for large scale computing.

**It seems that Rcpp has better results, and RcppArmadillo has been further optimized.**
