---
title: "Subsampling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Subsampling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You can get your subsample based various design-based methods, here we give some examples.
```{r setup}
library(dbsubsampling)
```

# Uniform Sampling
Get random subsample with equal probability.
```{r unif}
N <- 1000
n <- 10
Unif(N = 1000, n = 10)
```
You can set a random seed, this random seed is only valid for this sampling and will not affect the external environment. The parameter `replace` default `TURE` means the sampling is with replacement, you can set it 
`FALSE` to implement sampling without replacement.

```{r unif with seed}
Unif(N = 1000, n = 10, seed = 123, replace = TRUE)
```

# OSMAC
A subsampling method based on A- / L- optimal for logistic regression proposed by [Wang et.al. (2018)](https://www.tandfonline.com/doi/full/10.1080/01621459.2017.1292914)^[HaiYing Wang, Rong Zhu and Ping Ma (2018) *Optimal Subsampling for Large Sample Logistic Regression, Journal of the American Statistical Association, 113:522, 829-844*.].

## A-optimal
A-optimal minimise the trace of the covariance matrix of the parameter estimates.
```{r OSMAC-A}
data_binary <- data_binary_class
y <- data_binary[["y"]]
x <- data_binary[-which(names(data_binary) == "y")]

OSMAC(X = x, Y = y, r1 = 100, r2 = 10, method="mmse", seed_1 = 123, seed_2 = 456)
```
or you can use a unified interface(recommended):
```{r}
subsampling(y_name = "y", data = data_binary, n = 10, pilot_n = 100, method = "OSMAC_A", 
            seed_1 = 123, seed_2 = 456)
```

## L-optimal
L-optimal minimise the trace of the covariance matrix of the linear combination of parameter estimates.
```{r OSMAC-L}
OSMAC(X = x, Y = y, r1 = 100, r2 = 10, method="mvc", seed_1 = 123, seed_2 = 456)
```
or you can use a unified interface(recommended):
```{r}
subsampling(y_name = "y", data = data_binary, n = 10, pilot_n = 100, method = "OSMAC_L", 
            seed_1 = 123, seed_2 = 456)
```

*Tips: for uniform sampling you can use the unified interface such as:*
```{r}
subsampling(y_name = "y", data = data_binary, n = 10, method = "Unif", seed_1 = 123)
```

# IBOSS
A subsampling method based on D-optimal for linear regression proposed by [Wang et.al. (2019)](https://www.tandfonline.com/doi/full/10.1080/01621459.2017.1408468)^[HaiYing Wang, Min Yang & John Stufken (2019) Information-Based Optimal Subdata Selection for Big Data Linear Regression, Journal of the American Statistical Association, 114:525, 393-405.].
```{r}
data_numeric <- data_numeric_regression
X <- data_numeric[-which(names(data_numeric) == "y")]
IBOSS(n = 30, X = X)
```
or you can use a unified interface(recommended):
```{r}
subsampling(y_name = "y", data = data_numeric, n = 30, method = "IBOSS")
```

**We're working on more features，such as subsampling based on OSS, Lowcon, support point, etc. **
