---
title: "Subsampling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Subsampling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You can get your subsample based various design-based methods, here we give some examples.
```{r setup}
library(dbsubsampling)
```

# Uniform Sampling
Get random subsample with equal probability.
```{r unif}
N <- 1000
n <- 10
Unif(N = 1000, n = 10)
```
You can set a random seed, this random seed is only valid for this sampling and will not affect the external environment.

```{r unif with seed}
Unif(N = 1000, n = 10, seed = 123, replace = TRUE)
```

# OSMAC
A subsampling method based on A- / L- optimal for logistic regression proposed by [Wang et.al. (2018)](https://www.tandfonline.com/doi/full/10.1080/01621459.2017.1292914)^[HaiYing Wang, Rong Zhu and Ping Ma (2018) *Optimal Subsampling for Large Sample Logistic Regression, Journal of the American Statistical Association, 113:522, 829-844*.].

## A-optimal
A-optimal minimise the trace of the covariance matrix of the parameter estimates.
```{r OSMAC-A}
data <- data_binary_class
y <- data[["y"]]
x <- data[-which(names(data) == "y")]

OSMAC(X = x, Y = y, r1 = 100, r2 = 5, method="mmse", seed_1 = 123, seed_2 = 456)
```

## L-optimal
L-optimal minimise the trace of the covariance matrix of the linear combination of parameter estimates.
```{r OSMAC-L}
OSMAC(X = x, Y = y, r1 = 100, r2 = 5, method="mvc", seed_1 = 123, seed_2 = 456)
```

**We're working on more features，such as subsampling based on OSS, Lowcon, support point, etc. **
